Designing a Search for the BBC

### 2014-02-05 paper.tex
Moved into Springer format and fixed makefile as citations stopped working.

\documentclass[a4paper]{report}

@@

\title{Designing a Search for the BBC}
\author{Ross Fenning}

@@

\chapter{The Problem}

\section{Background}

@@

\section{Objectives}

@@

\chapter{Design}
\label{design}

\section{Use cases}

@@

\section{System Behaviour}

@@

\section{Domain Model}

@@

\section{Discussion and Analysis}
\label{appraisal}

xThe problem of
a BBC-wide search application was predicted --
and has certainly shown itself -- to be a very large-scale problem, the
full extent of which cannot be covered in this report. Thus it
is reasonable to conclude that the problem is not yet solved
at every level, but the high-level solutions are certainly promising.

@@

\chapter{Evaluation}
\label{evaluation}

@@

\appendix
\chapter{Proposal}

>>>>

\documentclass{llncs}

@@

\title{Designing a Search for the BBC}
\author{Ross Fenning}
\institute{BBC}

@@

\section{The Problem}

\subsection{Background}

@@

\subsection{Objectives}

@@

\section{Design}
\label{design}

\subsection{Use cases}

@@

\subsection{System Behaviour}

@@

\subsection{Domain Model}

@@

\subsection{Discussion and Analysis}
\label{appraisal}

The problem of
a BBC-wide search application was predicted --
and has certainly shown itself -- to be a very large-scale problem, the
full extent of which cannot be covered in this report. Thus it
is reasonable to conclude that the problem is not yet solved
at every level, but the high-level solutions are certainly promising.

@@

\section{Evaluation}
\label{evaluation}

@@

\appendix
\section{Proposal}
